---
title: "exercise1-3"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
## 3) Data visualization: flights at ABIA
```{r}
library(tidyverse)
library(ggplot2)
ABIA = read.csv(".../data/ABIA.csv")
```

**Overall:**

In 2008, a total of 49,623 flights are scheduled to depart from Austin, for which American Airlines and Southwest Airlines have the largest number of flights.

```{r}
library(tidyverse)
library(ggplot2)
Total_origin = ABIA %>%
  filter(Origin == 'AUS') %>%
  group_by(UniqueCarrier)%>%
  summarize(total_count = n())

summary(Total_origin)

ggplot(data = Total_origin) + 
  geom_col(mapping = aes(x=UniqueCarrier, y=total_count),fill = "blue")+
  labs(title="The number of flights that departure from AUS", 
       y="The number of flights",
       x = "Airlines")

```

By month, the number of flights departing from Austin in 2008 peaked in June, and then continued to decline until September. Even though the number of flights increased in October, the number of flights in November reached the lowest point of the year.

```{r}
origin_month = ABIA %>%
  filter(Origin == 'AUS') %>%
  group_by(Month)%>%
  summarize(flights = n())

origin_month

ggplot(data = origin_month) + 
  geom_line(mapping = aes(x=Month, y=flights),color = "blue")+
  scale_x_continuous(breaks = 1:12)+
  labs(title="Changes in the number of flights that departure from AUS (months)", 
       y="The number of flights",
       x = "Month")
```

To specific, the main factor that influenced the number of flights by month is that some airlines have drastically reduced the number of flights after June, and even no longer provide services, like EV, NW, OH, etc. 

```{r}
origin_month_carrier = ABIA %>%
  filter(Origin == 'AUS') %>%
  group_by(Month,UniqueCarrier)%>%
  summarize(flights = n())

origin_month_carrier


ggplot(data = origin_month_carrier) + 
  geom_line(mapping = aes(x=Month, y=flights,color=(UniqueCarrier)))+
  scale_x_continuous(breaks = 1:12)+
  scale_y_log10(breaks = c(2,4,20,40,100,200,900))+
  labs(title="Changes in the number of flights that departure from AUS (airlines)", 
       y="The number of flights",
       x = "Month")
```

**Flight delay without cancellation**

From the bar chart, we know that the airlines of EV and WN have the highest departure delay rates, and the departure delay rate of WN is even close to 50%.
```{r}
ABIA = ABIA %>%
  mutate(if_delay = ifelse(DepDelay > 0, 1, 0))
head(ABIA)

P1= ABIA %>%
  filter(Origin == 'AUS', Cancelled == 0) %>%
  group_by(UniqueCarrier) %>%
  summarize(total_count = n(),delay_num =sum(if_delay),delay_rate = delay_num/total_count)
P1

ggplot(data = P1) + 
  geom_col(mapping = aes(x=UniqueCarrier, y=delay_rate),fill = "blue")+
  labs(title="Delay Rate of Airlines in 2008", 
       y="Delay Rate",
       x = "Airlines")
```


From the line chart, we find that the departure delay rates on Tuesday and Saturday are the lowest, and the departure delay rates on Thursday and Friday are relatively higher than others.
```{r}
P2= ABIA %>%
  filter(Origin == 'AUS', Cancelled == 0) %>%
  group_by(DayOfWeek)%>%
  summarise(total_count = n(),delay_num =sum(if_delay),delay_rate = delay_num/total_count)
P2

ggplot(data = P2) + 
  geom_line(mapping = aes(x=DayOfWeek, y=delay_rate),color = "blue")+
  scale_x_continuous(breaks = 1:7)+
  labs(title="Delay Rate in 2008 (Day of Week) ", 
       y="Delay Rate",
       x = "Day of Week")
```



**The reason of cancellation** 

In 2008, the airline of EQ has the highest rate of cancellation, the airline of NW has the lowest rate of cancellation. 
```{r}
Total_origin_cancel = ABIA %>%
  filter(Origin == 'AUS') %>%
  group_by(UniqueCarrier)%>%
  summarize(total_count = n(),cancellation_num = sum(Cancelled), cancellation_rate = cancellation_num/total_count)

Total_origin_cancel

ggplot(data = Total_origin_cancel) + 
  geom_col(mapping = aes(x=UniqueCarrier, y=cancellation_rate),fill = "blue")+
  labs(title="Cancellation Rate of Airlines in 2008 ", 
       y="Cancellation Rate",
       x = "Airlines")
```


In the bar chart, there are three cancellation reasons(A = carrier, B = weather, C = NAS). Obviously, most cancellation is due to carrier.
```{r}
p4 = ABIA %>%
  filter(Origin == 'AUS',Cancelled==1) %>%
  group_by(CancellationCode)%>%
  summarize(total_count = n())
p4

ggplot(data = p4) + 
  geom_col(mapping = aes(x=CancellationCode,y=total_count),fill = "blue")+
  labs(title="Reasons for Cancellation in 2008 ", 
       y="The number of Cancellation",
       x = "Reasons")
```

Furthermore, among those carriers, we find that AA carrier has the largest number of cancellations. For carrier of AA, most of the reason for cancellation is because of the carrier itself; for carrier of WN, the number of cancellations due to reason B accounts for the majority.
```{r}
p5 = ABIA %>%
  filter(Origin == 'AUS',Cancelled==1) %>%
  group_by(CancellationCode,UniqueCarrier)%>%
  summarize(total_count = n())
p5

ggplot(data = p5) + 
  geom_col(mapping = aes(x=CancellationCode,y=total_count))+
  facet_wrap(~UniqueCarrier)+
  labs(title="The Reason of Cancellation", 
       y="The number of cancellation",
       x = "Cancellation Code",
       fill="CancellationCode")
```

**In conclusion:** if you want to depart from Austin by plane, you'd better avoid Tuesday and Saturday, and buy other airlines besides EV, WN and MQ.